Reply To Examiners

### 2014-05-05 answer_thesis_examiner/chap2.tex
auto

>>>>

\replyToComment
    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
    {Heteroskedastic and homoskedastic are terms defined in statistical context to respectively denote the fact that different sub-populations of a given samples can have different or similar variabilities. In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or the same variances.}

\replyToComment
    {Add references to the following statement: ``for example speckle filtering, target detection, image segmentation and other cluster, classification techniques''}
    {TODO:CITE}

\replyToComment
    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
    {TODO:CITE}

\replyToComment
    {Add references to the following statement: ``Such use, however, is known to be not very robust for these so-called heavy detailed distributions.''}
    {TODO:CITE}

\replyToComment
    {Add references to the following statement: ``it is known that such use should be avoided in preference to a ratio-based descrimination measure.''}
    {TODO:CITE}

\replyToComment
    {Add references to the following statement: ``The Ordinary Least Square (OLS) is widely used as the best evaluation criteria, which is probably due to the Gauss Markov theorem.''}
    {TODO:CITE}

\replyToComment
    {Add references to the following statement: ``violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.''}
    {TODO:CITE}

\replyToComment
    {It would be easier to read and refer if all the Equations are labelled accordingly.}
    {All equations in the thesis has been updated with labels.}

\textbf{Errata Sheet}
